ABC inferences

### 2024-12-19 application_examples/abc_inferences/draft-abc-inferences-vignette.Rmd
Updating changes before pulling

@@

# Add points colored by 'str' (0 for non-island, 1 for island)
points(filtered_data$start, filtered_data$CpG_density, 
       col = ifelse(filtered_data$str == 1, "red", "blue"), 
       pch = 16)  # pch=16 gives filled circles

>>>>

**IMPORTANT: BOTH HERE AND IN CFTP ENVIRONMENT.YAML BEFORE SUBMITTING CHANGE DEVTOOLS BY METHEVOLSIM**

@@

# Add points colored by 'str' (0 for non-island, 1 for island)
points(filtered_data$start, filtered_data$CpG_density, 
       col = ifelse(filtered_data$str == "Island", "red", "blue"), 
       pch = 16)  # pch=16 gives filled circles
